Preferences for the commodification of pensions in Chile: the rol of intergenerational social mobility

### 2025-12-01 paper/paper.tex
Up V1 borrador final
Up borrador VF1

% Colores extra por nombre
\usepackage[dvipsnames]{xcolor}
% Ajustes de hipervínculos
% \hypersetup{
%   colorlinks = true,
%   citecolor  = DarkSlateBlue,     % << citas
%   urlcolor   = DarkSlateBlue  % URLs/DOIs
% }
% 
\begin{document}
\maketitle
\begin{abstract}
My abstract \newline \textbf{Keywords}: Pension commodification ·
Intergenerational mobility · Causal inference · Meritocracy · Chile
\end{abstract}

\setstretch{1.5}
This document was last modified at 2025-12-01 02:26:24 and it was last
rendered at 2025-12-01 02:26:24.

>>>>

% Paquete para colores
\usepackage{xcolor}

% Definir color en formato HEX
\definecolor{mylinkcolor}{HTML}{3827a1}

% Ajustes de hipervínculos
\hypersetup{
  colorlinks = true,       % activar links coloreados
  linkcolor  = mylinkcolor,
  citecolor  = mylinkcolor,
  urlcolor   = mylinkcolor
}
\begin{document}
\maketitle
\begin{abstract}
My abstract \newline \textbf{Keywords}: Pension commodification ·
Intergenerational mobility · Causal inference · Meritocracy · Chile
\end{abstract}

\setstretch{1.5}
This document was last modified at 2025-12-01 02:47:28 and it was last
rendered at 2025-12-01 02:47:28.
